Inefficient Concessions and Mediation

### 2016-11-29 presentation.tex
date/title/author modifications to presention

\begin{document}
\title[Unrecognized States: A Theory of Self-Determination and Foreign Influence\hspace{1.25in}\insertframenumber/\inserttotalframenumber]{Unrecognized States: A Theory of Self-Determination and Foreign Influence}
\author[Kristy Buzard, Benjamin Graham and Ben Horne]{Kristy Buzard, Benjamin Graham and Ben Horne\\ kbuzard@syr.edu}
\date{September 23, 2016}
\maketitle
%\insertpresentationendpage removed b/c of appendix

@@

\section{Model}
\subsection{Economic and Political Structure}
\begin{frame}{Timeline}
\pause
\begin{figure}
\includegraphics[width=\linewidth,height=\textheight,keepaspectratio]{Timeline2.pdf}
%\caption{Timeline}
\end{figure}
\end{frame}

>>>>

\begin{document}
\title[Inefficient Concessions and Mediation\hspace{2.95in}\insertframenumber/\inserttotalframenumber]{Inefficient Concessions and Mediation}
\author[Kristy Buzard and Ben Horne]{Kristy Buzard and Ben Horne\\ kbuzard@syr.edu}
\date{December 3, 2016}
\maketitle
%\insertpresentationendpage removed b/c of appendix

@@

\section{Model}
\subsection{Economic and Political Structure}
\begin{frame}{Timeline}
\pause
\end{frame}
